Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-09-09 tex/paper1/paper1.tex
test changes to how the fit is calculated; also some edits to the paper

\subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
The first contribution to both models $M_{1}$ and $M_{2}$ is a
\PL-like \PS.  It is present in both wavebands studied and in all the
regions, and so parsimony suggests that the mechanism of its creation
is both similar and ubiquitous in all {\bf similar} parts of the solar
atmosphere {\bf , that is quiet Sun, moss, loop footpoints and above
  sunspots}.  Further, \cite{2014AA...563A...8A} show that a
\PL\ \PS\ is present in coronal active region and quiet Sun
time-series over the frequency range 0.01 - 1 mHz, overlapping with
the frequency studied in this paper.

{\bf \PL\ \PS\ have been observed in other solar phenomena.}

>>>>

\subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
The first contribution to both models $M_{1}$ and $M_{2}$ is a
\PL-like \PS.  It is present in both wavebands studied and in all the
regions, and so parsimony suggests that the mechanism of its creation
is both similar and ubiquitous in all {\bf similar} parts of the solar
atmosphere {\bf , that is quiet Sun, moss, loop footpoints and above
  sunspots}.  Further, \cite{2014AA...563A...8A} show that a
\PL\ \PS\ is present in time-series of coronal active region and quiet
Sun emission over the frequency range 0.01 - 1 mHz, overlapping with
the frequency studied in this paper.

{\bf \PL\ \PS\ have been observed in other solar phenomena.  Recently,
\citet{gupta2014} showed \PL\ \PS\ in coronal plumes extending over
}
